Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
Edits to concluding paragraph.

Finally, we note that this radio emission could studied through follow-up observations of known RGHJs or could be used as a tool for discovery, given the lowered sensitivity of radial velocity methods in detecting planetary companions. 
Once the planetary radio emission is detected, it will provide a unique approach for inferring the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.

>>>>

Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, that traditional exoplanet-discovery methods (e.g., transit or RV) are not very sensitive to planets around RGB or AGB stars.
Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.
